---
title: "Report"
author: "Andrew Liu, Carol Wang, Luna_Lan, Sarah Hu, Ziyi An"
date: "2/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("recover_rate.R")
```

## Problem Domain

Recently, influenced by COVIS-19 pneumonia, Chinese state-backed importers of natural gas are examining if they can provisionally halt contracts for the supercooled fuel, as the COVIS-19 outbreak depresses energy demand in the world’s second-largest economy. This temporary cancellation of contracts has created headaches for natural gas suppliers and made them concerned about the future.

Therefore, our group will discuss the correlation between spreading of COVIS-19 and the price of natural gas in the final project. This topic is meaningful because natural gas is one of the most important resources in the world and its market is closely tied to the global economy and to our daily life. The data of COVIS-19 virus spreading is from the World Health Organization and the data of natural gas prices is from datahub. They are all credible and sources. 

Only very basic statistical knowledge will be involved in our report and it should be straightforward for every reader!

### The List of Questions Covered:

#### 1. Based on the data set, does the number of coronovirus pneumonia cases confirmed have no effect on the price of natural gas?

Since we have many features describing the spreading of coronavirus, we need to find out which feature could have the most direct impact on the price of natural gas.


#### 2. 



#### 3. 



#### 4. Based on the data set, how is each country dealing with this issue? 
**(i.e.: What is the comparison of the recovery rate among all countries/regions?)**

This question is interesting because we will then be able to gain a sense of how people are taking control of the issue and which country could potentially have a better medical system or technology.

I first pull the data of Conoravirus case by the getVirus function we created. I also get the data of the world map through wbstats package. Then I added iso3c code to each data set so they can join later.(There is no iso3c code for "Mainland China" so I combined the data from Mainland china, Hongkong, Macau and Taiwan into "China".) In order to get the recover rate among each countries/region, I then grouped the countries/region, used the summary feature in dplyr package to sum up the confirmed cases and also the recover cases. Then I added a column calculating the percentage of recover rate. After this, I used left.join to combine the virus dataset with the world map dataset, then use ggplot to create a visualization for it.

```{r recovery, echo=FALSE}
plot(recover_compare)
```

**Result:** 

The darker the color, the lower the recovery rate is. For countries/regions that have over 100 confirmed cases, Italy, South Korea, Canada, the US, and China are five countries that have a lower recovery rate. China, with its vast confirmed case (1201794) and its 15% recovery rate, has a moderate level of control policies and significant medical resources support. However, countries like Italy with its 1.02% recovery rate, South Korea with its 8% recovery rate, Canada with its 10.77% recovery rate, and the US with its 12.81% recovery rate should pay more attention to this issue and provide more medical resources for their citizens.

**Evaluation:** 
According to the coronavirus data, it is clear that because the outbreak of the virus in different countries takes time, every region are at a different stage right now. We are still in the middle of the epidemic, and the data are updating every day, which means that the results we got now are not the latest and might not valid in the future.


#### 5. 
