---
title: "Report"
author: "Andrew Liu, Carol Wang, Luna_Lan, Sarah Hu, Ziyi An"
date: "2/25/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
source("analysis.R")
library("knitr")
corr <- correlation
corr2 <- correlation_volume
```

## Problem Domain

Recently, influenced by COVIS-19 pneumonia, Chinese state-backed importers of natural gas are examining if they can provisionally halt contracts for the supercooled fuel, as the COVIS-19 outbreak depresses energy demand in the world’s second-largest economy. This temporary cancellation of contracts has created headaches for natural gas suppliers and made them concerned about the future.

Since natural gas is one of the three most important fossil fuels, the natural gas market could have a large impact on the global economy. Therefore, our group will discuss the correlation between the spreading of COVIS-19 and two important economic indicators, price of natural gas and NBEV stock, in the final project. NBEV stock is an important but relatively risky stock which could reflect the stability of the stock market. If the price of NBEV goes down, it’s probably because investors become concerned about the future economy in the short run.

Only very basic statistical knowledge will be involved in our report and it should be straightforward for every reader!


### The List of Questions Covered:

#### 1. Based on the data set, does the number of coronovirus pneumonia cases confirmed have no effect on the price of natural gas?

Since the outbreak of coronavirus has raised concerns of suppliers of natural gas, it is meaningful to explore the relationship between natural gas prices and confirmed cases number.

In this question, we use simple regression model and correlation to solve this problem.The data of COVIS-19 virus spreading is from the World Health Organization(https://www.kaggle.com/sudalairajkumar/novel-corona-virus-2019-dataset) and the data of natural gas prices is from datahub(https://datahub.io/core/natural-gas). They are all credible and sources. 

Under the simple regression model, we can get a graph of the number of confirmed cases and the price of natural gas.
```{r echo=FALSE}
reg
```

The correlation of these two factor is `r corr`,which is a quite small number, indicating that based on the data we obtained, natural gas price seems to be unrelated with the number of cases confirmed statistically. Even though this conclusion seems to contradict with the economic expectation, it is explainable because currently, we have very limited statistics of coronavirus spreading. Restricted by the small pool of data, it is possible that our conclusion is not consistent with the long-term trend.


#### 2. Based on the data set, what is the effect of the number of coronavirus pneumonia cases confirmed have on the volume of the stock trade of [company]? 
**(i.e.: To what extent are the coronavirus pneumonia cases affecting the willingness that people have to participate in the economy.)**

We would like to find out if people’s willingness to participate in the economy is an issue and if there is anything we need to do about it, considering the severity of the coronavirus.

In this question, we use simple regression model and correlation to solve this problem.The data of COVIS-19 virus spreading is from the World Health Organization(https://www.kaggle.com/sudalairajkumar/novel-corona-virus-2019-dataset). The data of stock trade is a table with date matched to a summary of trades that happened on that day. It includes, high, low, volume, open price, and closing price. It is retrieved from the yahoo finance api (https://rapidapi.com/apidojo/api/yahoo-finance1, end point stock/get-histories) and parsed into an expected format.

**Data analysis method: **
I pulled out the stock data for China first(from 2020-01-22 to 2020-02-20), and also the data of COVIS-19. Then I calculated the mean value of confirmed cases for each date that was included and put that into a seperate data frame. Since there are some dates missing in the stock data frame, for clarity and simplicity, I droped some rows in the confirmed cases table to match the number of rows in stock data frame so that it's easier to join and analysis. Then I put the information on these two tables together, and draw the graph that shows the relationship between volume of stock and the number of confirmed cases for COVIS-19.

```{r echo=FALSE}
reg_volume
```

**Result: **
The correlation of these two factor is `r corr2`, it's slightly more than 0.5 which gets closer to 1. This value indicates that based on the data we obtained, number of confirmed cases and the volume of stock are related, but not related in large extent.

**Evaluation: ** 
The result answers the question that there definitely have correlations between number of confirmed cases of coronavirus and the volume of stock, which means the number of confirmed cases will largely affect people's willingness to participate in the economy. It's explainable because the data size we are using is not very large, and some dates are not included due to some reasons in colleting data, the trend in the future might not be same, and there will likely have variations based on location and time.

#### 3. 



#### 4. Based on the data set, how is each country dealing with this issue? 
**(i.e.: What is the comparison of the recovery rate among all countries/regions?)**

This question is interesting because we will then be able to gain a sense of how people are taking control of the issue and which country could potentially have a better medical system or technology.

I first pull the data of Conoravirus case by the getVirus function we created. I also get the data of the world map through wbstats package. Then I added iso3c code to each data set so they can join later.(There is no iso3c code for "Mainland China" so I combined the data from Mainland china, Hongkong, Macau and Taiwan into "China".) In order to get the recover rate among each countries/region, I then grouped the countries/region, used the summary feature in dplyr package to sum up the confirmed cases and also the recover cases. Then I added a column calculating the percentage of recover rate. After this, I used left.join to combine the virus dataset with the world map dataset, then use ggplot to create a visualization for it.

```{r recovery, echo=FALSE}
plot(recover_compare)
```

**Result:** 

The darker the color, the lower the recovery rate is. For countries/regions that have over 100 confirmed cases, Italy, South Korea, Canada, the US, and China are five countries that have a lower recovery rate. China, with its vast confirmed case (1201794) and its 15% recovery rate, has a moderate level of control policies and significant medical resources support. However, countries like Italy with its 1.02% recovery rate, South Korea with its 8% recovery rate, Canada with its 10.77% recovery rate, and the US with its 12.81% recovery rate should pay more attention to this issue and provide more medical resources for their citizens.

**Evaluation:** 
According to the coronavirus data, it is clear that because the outbreak of the virus in different countries takes time, every region are at a different stage right now. We are still in the middle of the epidemic, and the data are updating every day, which means that the results we got now are not the latest and might not valid in the future.


#### 5. 


## Data Description
We are using two datasets: one is the novel coronavirus dataset which contains the records of value for the confirmed case, recovered case and death case from different districts over the world by date; another is the economic change dataset which contains the value for natural gas trade and the US stock market value within the same time zone as the coronavirus. 

We got the novel coronavirus dataset from [Kaggle](https://www.kaggle.com/sudalairajkumar/novel-corona-virus-2019-dataset). The data originally comes from Johns Hopkins University. One note about this dataset is that it’s time series data.

```{r echo=FALSE}
kable(virus_sample)
```

In the above table: Confirmed, Death, Recovered are the number of the Confirmed, Death, Recovered found in Province.State of Country.Region on that Date. The unit is person.

The data of stock trade is a table with date matched to a summary of trades that happened on that day. It includes, high, low, volume, open price, and closing price. It is retrieved from the [yahoo finance api](https://rapidapi.com/apidojo/api/yahoo-finance1), end point "stock/get-histories" and parsed into an expected format. It is joined with the data of natrual gas by date. The data of natrual gas is retrived from [datahub](https://datahub.io/core/natural-gas), that is collected from U.S. Energy Information Administration EIA Dataset.

```{r echo=FALSE}
kable(stock_sample)
```

In the above table: low, high, close, open is the lowest price, highest price, closing price, and opening price in USD of "NBEV" on that date, price is the price of natural gas in USD. Volume is the volume of trade of "NBEV" on that date.
